\documentclass[7pt]{article}

\usepackage{amsmath}
\usepackage[margin=.25in, landscape]{geometry}
\usepackage[ruled, vlined]{algorithm2e}
%\usepackage{algorithmic}
\usepackage{multicol}

\linespread{1}
\begin{document}

\begin{multicols*}{4}
\subsection*{Automata}

\subsubsection*{Pumping Lemma for regular languages}
If $A$ is a regular language, then there is number $p$ (the pumping length) where, if $s$ is any string in $A$ of at least $p$, then $s$ may be divided into three pieces, $s = xyz$, satisfying the following conditions:
\begin{enumerate}
\item for each $i \geq 0$, $xy^iz \in A$
\item $|y| > 0$, and
\item $|xy| \leq p$
\end{enumerate}

Ways to solve (both handl negative weight edges): 
\begin{itemize}
\item Fast Matrix Multiplication ($\theta(|V|^3log|V|)$)
\item Floyd Warshall: $(\theta(|V|^3))$
\end{itemize}

\subsubsection*{Matrix Multiplication}
Basic idea: Find min weight of any path from i to j that uses at most
$m$ edges ($m$ being an iterator from $1..n$).  

\begin{itemize}
\item Uses optimal substructure to get recursive definition (is there
  an intermediate node that will shorten the path between i and j)
\begin{equation} l_{ij}^{(m)} = min_{1 \leq k \leq n}(l_{ik}^{(m-1)} +
  w_{kj})\end{equation}
\item Start with $L^{(1)} = W$ and compute new $L$s until $L^{(n-1)}$
  (n being the number of rows in L) 
\item  If $n^{th}$ iteration changes (new shortest path), there's a
  neg weight cycle
\item Faster APSP with MM alters the number of times needed to compute
  $L^{(n)}$.  Just compute $L^{(2m)}$ finding min of $l"_{ij}^{(m)}$,
  and $l_{ik}^{m} + l_{kj}^{m}$
\end{itemize}

\subsubsection*{Floyd-Warshall}
Basic idea: For each vertex $k$, find the shortest path between every
two vertices $i$ and $j$ using $k$ as a possible intermediary.  For
each iteration of $k$, the shortest path between $i$ and $j$ will be
the shortest path using the intermediate vertices $1..k-1$ (it could
be a direct path or any path using some $k$ as step between $i$ and
$j$).  

\subsubsection*{Transitive Closure}
For some directed, unweighted graph, does a path exist between i and
j?  Use FW: set edge weights to 0 if $i \neq j \wedge (i,j) \not\in E$ or
1 if $i = j \vee (i,j) \in E$ ($\theta(n^3)$).

\subsection*{Max Flow}
{\bf Flow Network:} D-graph where each edge has nonnegative capacity
(typically connected)
{\bf Flow:} Some assignment of real numbers to each edge where the
capacity constraint and flow conservation hold.


\begin{itemize}
\item Capacity: Should be nonnegative and not exceed capacity
\item Flow Cons.: Sum of flows entering vertex is equal to sum of flows
leaving vertex
\item Value of the flow for the graph is the sum of all flow leaving the
start vertex.
\item Multiple sources/sinks can be combined into one
  pseudo-sink/source with capacities of infinity connecting them
\end{itemize}

\subsubsection*{Ford-Fulkerson}
$O(|E|f*)$

\begin{itemize}
\item Creates residual network, which is the same network with
  capacities reduced based on amount of flow going through it
\item An edge U----5/9---$>$V in the original flow would have two edges
  in the residual U----4/9---$>$V and U$<$----5/9---V
\item Algorithm Outline:
  \begin{itemize}
  \item Take initial graph with flow of 0, find augmenting path (a
    simple path through the residual network).  
  \item Find smallest capacity on augmenting path and add that
    capacity to each corresponding edge in the original flow (i.e.,
    augment the flow).
  \item Repeat until no augmenting paths are found
  \end{itemize}
\end{itemize}

\subsubsection*{Edmonds-Karp}
$O(|V||E|^2)$

Same as FF except always choose shortest path (edge count) for
augmenting path.

\subsubsection*{Maximum Bipartite matching}
$O(|V||E|)$

Basic idea is to create a dummy root node with infinite capacities
going to each vertex on the left of the bipartite graph, and a finish
node on the right.  Each edge between already existing vertices has a
capacity of 1.  Max flow will show the highest number of edges matched
between the two sets of vertices.  

\subsubsection*{Max-Flow Min-Cut}
\begin{itemize}
\item Used to prove that if there's an augmenting path, flow can be
  increased
\item Net flow across a cut is the sum of all forward edges minus the
  sum of all back edges across the cut
\item Capacity of the cut are the sum of every forward edge
\item Proof (truncated):
  \begin{enumerate}
  \item $f$ is a max flow in $G$
  \item $G_f$ has no augmenting paths
  \item $|f| = c(S,T)$ for some (i.e., minimum) cut $(S,T)$ of $G$
  \end{enumerate}

  Show that $1->2->3->1$
\end{itemize}
\subsection*{NP-Completeness}

{\bf Show a problem is in NPC}
\begin{itemize}
\item Show it's in NP by showing it's verifiable in poly time using
  some certificate
\item Reduce \emph{from} any known NPC problem (all possible instances
  of one) to the unknown NPC problem in poly time.
\end{itemize}

{\bf NPC problems to reduce from}
\begin{itemize}
\item HAM-CYCLE: Does a graph $G$ have a Ham-cycle (a simple cycle
  that visits every vertex exactly once)?
\item CIRCUIT-SAT: Is there a satisfying assignment of inputs to a
  circuit that makes it output 1?
\item SAT: Does some boolean formula have a set of satisfying assignments?
\item 3-CNF-SAT: Ditto, but the SAT takes on the specific form of
  $(x_k \wedge x_j \wedge x_i) \vee (x_k \wedge x_v \wedge x_l) ...$
\item CLIQUE: Does graph $G$ contain a clique of size $k$?
\item VERTEX-COVER: Does graph $G$ have a set of $k$ vertices that
  touch every edge
\item TSP: Does a complete, weighted graph $G$ have a HamCycle of
  total weight $\leq k$?
\item SUBSET-SUM: Is there a subset of integers from $S$ that some to
  exactly $t$? 
\end{itemize}

\subsection*{Dynamic Programming}
Basic idea: Decompose a problem into subproblems, resuing overlapping
solutions to the subproblems.

\subsubsection*{Rod Cutting}
Goal: Cut rod of length $n$ into smaller rods to maximize profit (cuts
occur at integral boundaries).  Using optimal substructure, can find
the optimal size of cuts.

{\bf Top-down with memoization}: Start with some recurisve formula, but
for each call, check to see if the result for that call has already
been computed.
\end{multicols*}
\begin{figure*}[ttt!] %Still no idea what the 'ttt!' does
  \begin{minipage}[t]{.25\linewidth}
    \vspace{0pt}
    
    {\bf Bottom-up}: Start with small subproblems, then build up the
    solution.
    
    {\bf Solution for rod cutting - memoized}: ($\theta(n^2)$) If the solution for the
    current call hasn't already been found, find the max profit of every
    cut of the current length from cut of size 1 to $n$ plus the max
    profit of all possible cuts using the uncut portion.   
    
    \begin{algorithm}[H]
      \caption{Print-All-Pairs-Shortest-Path($\Pi,i,j$)}
      \uIf{$i==j$}{
        print $i$ 
      }
      \uElseIf{$\pi_{ij}==$ {\sc nil}}{
        print ``no path from '' $i$ `` to '' $j$ `` exists'' 
      }
      \uElse{
        {\sc Print-All-Pairs-Shortest-Path}$(\Pi,i,\pi_{ij})$ 
        print $j$ 
      }
    \end{algorithm}
    
    \begin{algorithm}[H]
    \caption{Extend-Shortest-Paths($L,W$)}
      $n=$ number of rows of $L$  \hspace*{0.25in} // This is $L^{(m)}$ 

      create new $n \times n$ matrix $L'$ \hspace*{0.125in} // This will be
$L^{(m+1)}$ 

      \For{$i=1$ to $n$}{
          \For{$j=1$ to $n$}{
              $\ell_{ij}' = \infty$ 

              \For{$k=1$ to $n$}{
                  $\ell_{ij}' = \min \left( \ell_{ij}', \ell_{ik}+w_{kj} \right)$
              }
          }
      }
      {\bf return} $L'$ 
    \end{algorithm}

    \begin{algorithm}[H]
    \caption{Slow-All-Pairs-Shortest-Paths($W$)}
      $n=$ number of rows of $W$ 

      $L^{(1)}=W$ 

      \For{$m=2$ to $n-1$}{
          $L^{(m)}=$ {\sc Extend-Shortest-Paths}$(L^{(m-1)},W)$ 
      }
      {\bf return} $L^{(n-1)}$ 
    \end{algorithm}

  \end{minipage}
  \begin{minipage}[t]{.25\linewidth}
    \vspace{0pt}

    \begin{algorithm}[H]
    \caption{Faster-All-Pairs-Shortest-Paths($W$)}
      $n=$ number of rows of $W$ 

      $L^{(1)}=W$ 

      $m=1$ 

      \While{$m< n-1$}{
          $L^{(2m)}=$ {\sc Extend-Shortest-Paths}$(L^{(m)},L^{(m)})$ 

          $m=2m$ 
      }
      {\bf return} $L^{(m)}$ 
    \end{algorithm}


    \begin{algorithm}[H]
    \caption{Floyd-Warshall($W$)}
      $n=$ number of rows of $W$ 

      $D^{(0)}=W$ 

      \For{$k= 1$ to $n$}{
         \For{$i= 1$ to $n$}{
             \For{$j= 1$ to $n$}{
                $d_{ij}^{(k)}  = \min \left( d_{ij}^{(k-1)} , d_{ik}^{(k-1)} +
d_{kj}^{(k-1)} \right)$
              }
          }
      }
      {\bf return} $D^{(n)}$ 
    \end{algorithm}
    
    \begin{algorithm}[H]
    \caption{Transitive-Closure($G$)}
      allocate and initialize $n \times n$ matrix $T^{(0)}$ 

      \For{$k= 1$ to $n$}{
         allocate $n \times n$ matrix $T^{(k)}$ 

         \For{$i= 1$ to $n$}{
             \For{$j= 1$ to $n$}{
                $t_{ij}^{(k)}  =  t_{ij}^{(k-1)} \vee t_{ik}^{(k-1)} \wedge
t_{kj}^{(k-1)} $
              }
          }
      }
      {\bf return} $T^{(n)}$ 
    \end{algorithm}

   \begin{algorithm}[H]
   \caption{Ford-Fulkerson-Method($G,s,t$)}
    Initialize flow $f$ to 0 \;
    \While{there exists augmenting path $p$ in residual network $G_f$}{
        augment flow $f$ along $p$ \;
    }
     {\bf return} $f$ \;
   \end{algorithm}
    
  \end{minipage}
  \begin{minipage}[t]{.25\linewidth}
    \vspace{0pt}
   \begin{algorithm}[H]
   \caption{Ford-Fulkerson($G,s,t$)}
    \For{each edge $(u,v)\in E$}{
           $f(u,v)=0$ \;
    }
    \While{there exists path $p$ from $s$ to $t$ in $G_f$}{
        $c_f(p) = \min \{c_f(u,v) : (u,v) \mbox{ is in $p$} \}$ \;
        \For{each edge $(u,v) \in p$}{
            \uIf{$(u,v) \in E$}{
                $f(u,v)=f(u,v)+c_f(p)$ \;
             }
            \uElse{
                $f(v,u)=f(v,u)-c_f(p)$ \;
             }
         }
    }
   \end{algorithm}


    \begin{algorithm}[H]
    \caption{Memoized-Cut-Rod-Aux($p,n,r$)}
        \uIf{$r[n] \ge 0$}{
            {\bf return} $r[n]$   \hspace*{0.5in} // $r$ initialized to all $-\infty$ \;
         }
        \uIf{$n==0$}{
            $q=0$ \;
         }
        \uElse{
          $q=-\infty$ \;
           \For{$i=1$ to $n$}{
             $q=\max (q, p[i] +$
               $ \mbox{\sc Memoized-Cut-Rod-Aux}(p,n-i,r))$
             }
          $r[n]=q$ \;
         }
    {\bf return} $q$ \;
    \end{algorithm}

    \begin{algorithm}[H]
    \caption{Bottom-Up-Cut-Rod($p,n$)}
        Allocate $r[0\ldots n]$ \;
        $r[0]=0$ \;
         \For{$j=1$ to $n$}{
          $q=-\infty$ \;
           \For{$i=1$ to $j$}{
             $q=\max \left(q, p[i] + r[j-i]  \right)$
             }
          $r[j]=q$ \;
         }
    {\bf return} $r[n]$ \;
    \end{algorithm}
  \end{minipage}
  \begin{minipage}[t]{.25\linewidth}
    \vspace{0pt}

    \begin{algorithm}[H]
    \caption{Extended-Bottom-Up-Cut-Rod($p,n$)}
        Allocate $r[0\ldots n]$ and $s[0\ldots n]$ \;
        $r[0]=0$ \;
         \For{$j=1$ to $n$}{
          $q=-\infty$ \;
           \For{$i=1$ to $j$}{
                \uIf{$q<p[i] + r[j-i]$}{
                    $q=p[i]+r[j-i]$ \;
                     $s[j]=i$ \;
                 }
             }
          $r[j]=q$ \;
         }
    {\bf return} $r,s$ \;
    \end{algorithm}
    
    {\bf Reductions}:
    \begin{itemize}
    \item Circuit-Sat $\rightarrow$ SAT: For each input to the CS, create a
      variable in the SAT.  For each output of a logic gate, create a
      variable.  Clauses in the SAT are the ouput iff (input gate
      input gate ...). SAT is conjunction of clauses (including final
      output).     
    \item SAT $\rightarrow$ 3-CNF-SAT: Build a parse tree (outermost
      to innermost).  This gets it to at most 3 elements per clause.
      Then generate a truth table for the 3 elements, grab the ones
      that evaluate to 1, or them, use DeMorgan's.  
    \item 3-CNF-SAT $\rightarrow$ Clique: For each clause, make 3
      vertices (representing the variables in the clause).  Draw edges
      between vertices if the vertices aren't negations of each other
      and they aren't from the same clause.
    \item Clique $\rightarrow$ Vertex-Cover: Find the complement of
      the graph in the Clique problem.  $VC-k$ becomes $|V| - clique-k$
    \end{itemize}
    
  \end{minipage}
  
  
  
\end{figure*}
\end{document}